---
title: FFresearch
output: github_document
bibliography: BibTeX.bib
---
<style> body {text-align: justify} </style>

[![Travis-CI Build Status](https://travis-ci.org/bautheac/FFresearch.svg?branch=master)](https://travis-ci.org/bautheac/FFresearch)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/bautheac/FFresearch?branch=master&svg=true)](https://ci.appveyor.com/project/bautheac/FFresearch)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

```{r, `load`, include = FALSE}
library(FFresearch)
data(list = c("factors", "portfolios_univariate", "portfolios_bivariate", "portfolios_trivariate", 
              "portfolios_industries", "variables", "breakpoints"), 
     package = "FFresearch")
```


# FFresearch

Fama/French research data conveniently packaged for consumption by R users. The data is pulled directly from Kenneth French's online [data library](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html). Size concerns limit the data history to the last twenty years; the full time series are available from the author upon request. Install from [github](https://github.com/bautheac/FFresearch/) with `devtools::install_github("bautheac/FFresearch")`.


## portfolios

### univariate

The 'portfolios_univariate' dataset provides various feature time series for Fama/French portfolios formed on single variable sorts. Sorting variables include size, book-to-market, operating profitability and investment.

Dataset excerpt:
```{r, `portfolios_univariate`, echo = FALSE}
head(portfolios_univariate)
```

### bivariate

The 'portfolios_bivariate' dataset provides various feature time series for Fama/French portfolios formed on two variable sorts. Sorting variables include size, book-to-market, operating profitability and investment.

Dataset excerpt:
```{r, `portfolios_bivariate`, echo = FALSE}
head(portfolios_bivariate)
```

### trivariate

The 'portfolios_trivariate' dataset provides various feature time series for Fama/French portfolios formed on three variable sorts. Sorting variables include size, book-to-market, operating profitability and investment.

Dataset excerpt:
```{r, `portfolios_trivariate`, echo = FALSE}
head(portfolios_trivariate)
```


### industries

The 'portfolios_industries' dataset provides various feature time series for Fama/French industry portfolios [@fama_industry_1997].

Dataset excerpt:
```{r, `portfolios_industries`, echo = FALSE}
head(portfolios_industries)
```


## factors

The 'factors' dataset provides the return (factors) and level (ris free rate) time series for the classic Fama/French asset pricing factors as used in their three [@fama_cross_section_1992; @fama_common_1993; @fama_size_1995] and most recently five-factor [@fama_five_factor_2015; @fama_dissecting_2016; @fama_international_2017] asset pricing models extremely popular to the asset pricing enthousiasts.  

Dataset excerpt:
```{r, `factors`, echo = FALSE}
head(factors)
```


## variables

The 'variables' dataset is a helper dataset that provides details, including contruction methods, for the variables used to construct the portfolios and asset pricing factors above.

Dataset excerpt:
```{r, `variables`, echo = FALSE}
head(variables)
```

## breakpoints

The 'breakpoints' dataset is a helper dataset that provides the times series for the variables breakpoints used to construct the variables that in turn allow the construction of the portfolios and asset pricing factors above-mentioned.

Dataset excerpt:
```{r, `breakpoints`, echo = FALSE}
head(breakpoints)
```


#### References

