---
title: FFresearch
output: github_document
bibliography: literature_files/references.bib
---

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

```{r, `load`, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.path = "README-")

folder <- "literature_files"; dir.create(folder)
download.file("https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", paste(folder, "references.bib", sep = "/"))

library(FFresearch)
data(list = c("factors", "portfolios_univariate", "portfolios_bivariate", "portfolios_trivariate", 
              "portfolios_industries", "variables", "breakpoints"), 
     package = "FFresearch")
```

<style> body {text-align: justify} </style>


Fama/French research data conveniently packaged for consumption by R users. The data is pulled directly from Kenneth French's online [data library](http://mba.tuck.dartmouth.edu/pages/faculty/ken.french/data_library.html).   
Install from [github](https://github.com/bautheac/FFresearch/) with `devtools::install_github("bautheac/FFresearch")`.  


### Portfolios

#### Univariate
The 'portfolios_univariate' dataset provides various feature time series for Fama/French portfolios formed on single variable sorts. Sorting variables include size, book-to-market, operating profitability and investment:
```{r, `portfolios_univariate`, echo = FALSE}
head(portfolios_univariate)
```

#### Bivariate
The 'portfolios_bivariate' dataset provides various feature time series for Fama/French portfolios formed on two variable sorts. Sorting variables include size, book-to-market, operating profitability and investment. Size concerns limit the data history to the last ten years; the full time series are available from the author upon request.  
```{r, `portfolios_bivariate`, echo = FALSE}
head(portfolios_bivariate)
```

#### Trivariate
The 'portfolios_trivariate' dataset provides various feature time series for Fama/French portfolios formed on three variable sorts. Sorting variables include size, book-to-market, operating profitability and investment:
```{r, `portfolios_trivariate`, echo = FALSE}
head(portfolios_trivariate)
```


#### Industries
The 'portfolios_industries' dataset provides various feature time series for Fama/French industry portfolios [@fama_industry_1997]:
```{r, `portfolios_industries`, echo = FALSE}
head(portfolios_industries)
```


### Factors
The 'factors' dataset provides the return (factors) and level (risk free rate) time series for the classic Fama/French asset pricing factors as used in their three [@fama_cross_section_1992; @fama_common_1993; @fama_size_1995] and most recently five-factor [@fama_five_factor_2015; @fama_dissecting_2016; @fama_international_2017] asset pricing models extremely popular to the asset pricing enthusiasts:
```{r, `factors`, echo = FALSE}
head(factors)
```


### Variables
The 'variables' dataset is a helper dataset that provides details, including construction methods, for the variables used to construct the portfolios and asset pricing factors above:
```{r, `variables`, echo = FALSE}
head(variables)
```

### Breakpoints
The 'breakpoints' dataset is a helper dataset that provides the times series for the variables breakpoints used to construct the variables that in turn allow the construction of the portfolios and asset pricing factors above-mentioned:
```{r, `breakpoints`, echo = FALSE}
head(breakpoints)
```


## References

